An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2020-01-15 preprint/positive_results_SRs_RRs.Rmd
weird Git issue? I should be pulling these changes, not pushing them

## Disclosures
### Data, materials, and online resources
The data and code necessary to reproduce all analyses reported here, as well as the [Appendix](https://osf.io/vcqya/), the [preregistration document](https://osf.io/sy927/) and additional supplementary files, are available at <https://osf.io/dbhgr>. The manuscript including figures and statistical analyses, the Appendix, and the [codebook](https://osf.io/6jrkz/) available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.

>>>>

## Disclosures
### Data, materials, and online resources
The data and code necessary to reproduce all analyses reported here, as well as the [Appendix](https://osf.io/qw798/), the [preregistration document](https://osf.io/sy927/) and additional supplementary files, are available at <https://osf.io/dbhgr>. The manuscript including figures and statistical analyses, the [Appendix](https://osf.io/qw798/), and the [codebook](https://osf.io/6jrkz/) available in the supplement were created using RStudio [1.2.5019, @RStudioTeam2019] and `r my_citation`.

### 2020-01-15 preprint/positive_results_SRs_RRs.tex
weird Git issue? I should be pulling these changes, not pushing them

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/mainplot-1.pdf}
\caption{\label{fig:mainplot}Positive result rates for standard reports and Registered Reports. Error bars indicate \(95 \%\) confidence intervals around the observed positive result rate.}
\end{figure}

@@

{\centering \includegraphics[width=0.6\textwidth]{manuscript_files/figure-latex/powerbaserate-1}

@@

The data and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/vcqya/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration document} and additional supplementary files, are available at \url{https://osf.io/dbhgr}. The manuscript including figures and statistical analyses, the Appendix, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).

>>>>

\begin{figure}
\centering
\includegraphics{positive_results_SRs_RRs_files/figure-latex/mainplot-1.pdf}
\caption{\label{fig:mainplot}Positive result rates for standard reports and Registered Reports. Error bars indicate \(95 \%\) confidence intervals around the observed positive result rate.}
\end{figure}

@@

{\centering \includegraphics[width=0.6\textwidth]{positive_results_SRs_RRs_files/figure-latex/powerbaserate-1}

@@

The data and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration document} and additional supplementary files, are available at \url{https://osf.io/dbhgr}. The manuscript including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
